Analysis of the included studies

### 2023-03-15 epidemics_manuscript/outbreak_response_models_review_v2.tex

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.2in}

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Mechanistic modelling of outbreak response interventions to human vaccine-preventable diseases: a systematic review of modelling practices before COVID-19}
}
\newline
\\
James M. Azam\textsuperscript{1*},
Xiaoxi Pang\textsuperscript{2},
Elisha B. Are\textsuperscript{1, 3},
Juliet R.C. Pulliam\textsuperscript{1},
Matthew J. Ferrari\textsuperscript{4}
\\
\bigskip
\textbf{1} DSI-NRF Centre of Excellence in Epidemiological Modelling and Analysis (SACEMA), Stellenbosch University, Stellenbosch 7600, South Africa
\\
\textbf{2} Department of Mathematics, The University of Manchester, Manchester, UK
\\
\textbf{3} Department of Mathematics, Simon Fraser University, Burnaby, BC, Canada
\\
\textbf{4} Center for Infectious Disease Dynamics, Department of Biology, The Pennsylvania
State University, University Park, Pennsylvania, USA
\\
\bigskip

### 2023-04-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Changed output to pdf
Removed redundant loaded packages and changed global chunk settings

---
title: "Analysis of the included studies"
output:
  word_document:
    toc: yes
  pdf_document:
    toc: yes
    keep_tex: yes
    fig_crop: no
---

```{r echo=FALSE, include=FALSE}
#' load packages
library('tidyverse')
library('readr')
library('ggthemes')
library('mdthemes')
library('scales')
library('janitor')
library('forcats')
library('stringr')
library('countrycode')
library('bib2df')
library('conflicted')
library('Hmisc')
library('ggwordcloud')

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(dev = 'jpeg')
knitr::opts_chunk$set(out.height = "\\textheight",  out.width = "\\textwidth")
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)

#create a folder for storing the manuscript figures

>>>>

---
title: "Analysis of the included studies"
output:
  # word_document:
  #   toc: yes
  pdf_document:
    toc: yes
    keep_tex: yes
    fig_crop: no
---

```{r echo=FALSE, include=FALSE}
#' load packages
library('tidyverse')
library('ggthemes')
library('mdthemes')
library('scales')
library('janitor')
library('countrycode')
library('bib2df')
library('conflicted')
library('Hmisc')
library('ggwordcloud')

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      dev = 'png', 
                      out.height = "\\textheight",  
                      out.width = "\\textwidth", 
                      message = FALSE, 
                      warning = FALSE
                      )
```

```{r}
#create a folder for storing the manuscript figures
